### 2024-02-20 paper_sisc_first_revision/localpsf.tex
incorporated Omar's comments

In Table~\ref{tab:frog_psf_vs_hodlr_vs_glr} we compare the
computational cost to approximate the blur kernel from
Equation~\eqref{eq:frog_kernel} using the PSF-based method, the
randomized HODLR (hierarchical off diagonal low rank)
method~\cite{Martinsson16,Hartland_2023} with 8 hierarchical levels, and GLR (global low rank)
approximation using double-pass randomized SVD~\cite{HalkoMartinssonTropp11}. For
these results we vary the quantity $L$ to scale the width of the
impulse responses and hence the rank of the operator. For each case,
we calculate the relative error in the approximation of the kernel
measured in the Frobenius norm, $||\boldsymbol{\Phi} -
\widetilde{\boldsymbol{\Phi}}||_\text{Fro} /
||\boldsymbol{\Phi}||_\text{Fro}$ and show the number of operator
applications required to achieve 20\%, 10\%, and 5\% relative error by
each method. The results reveal superior performance of the PSF
method as compared to the HODLR and GLR methods for all cases. We note
that as we increase the rank and decrease the error tolerance, the
performance of the the HODLR and GLR methods deteriorates.

@@

In Figure \ref{fig:PSF_tau_convergence} we show the convergence of the PSF-based method on the blur kernel as a function of the total number of impulse responses (left), and the number of batches (right). We show convergence for several ellipsoid size parameters $\tau$, ranging from $2.0$--$4.0$. The results in Figure \ref{fig:PSF_tau_convergence} (left) show that the relative error decreases as $\text{constant} \times \left(\# \text{impulse responses}\right)^{-1}$
% or $\text{constant} \times \# \text{batches}^{-1}$, 
suggesting linear convergence. The linear convergence stalls at a limit which depends on $\tau$. Increasing $\tau$ lowers this limit, allowing the PSF-based method to achieve higher accuracy. 
In Figure \ref{fig:PSF_tau_convergence} (right), the results show that before this limit is reached, the convergence is faster for smaller $\tau$ in terms of the number of batches. This is expected because smaller $\tau$ results in more impulse responses per batch. Larger $\tau$ causes the PSF-based method converge more slowly than smaller $\tau$, but with larger $\tau$ the PSF-based method stalls at a lower level of error than it does with smaller $\tau$ (see, e.g., $\tau=4.0$ vs. $\tau=2.5$).

>>>>

In Table~\ref{tab:frog_psf_vs_hodlr_vs_glr} we compare the
computational cost to approximate the blur kernel from
Equation~\eqref{eq:frog_kernel} using the PSF-based method, the
randomized HODLR (hierarchical off diagonal low rank)
method~\cite{Martinsson16,Hartland_2023} with 8 hierarchical levels, and GLR (global low rank)
approximation using double-pass randomized SVD~\cite{HalkoMartinssonTropp11}. For
these results we vary the quantity $L$ to scale the width of the
impulse responses and hence the rank of the operator. For each case,
we calculate the relative error in the approximation of the kernel
measured in the Frobenius norm, $||\boldsymbol{\Phi} -
\widetilde{\boldsymbol{\Phi}}||_\text{Fro} /
||\boldsymbol{\Phi}||_\text{Fro}$ and show the number of operator
applications required to achieve 20\%, 10\%, and 5\% relative error by
each method. The results reveal superior performance of the PSF
method as compared to the HODLR and GLR methods for all cases. We note
that as we increase the rank and decrease the error tolerance, the
performance of the HODLR and GLR methods deteriorates.

@@

In Figure \ref{fig:PSF_tau_convergence} we show the convergence of the PSF-based method on the blur kernel as a function of the total number of impulse responses (left), and the number of batches (right). We show convergence for several ellipsoid size parameters $\tau$, ranging from $2.0$--$4.0$. The results in Figure \ref{fig:PSF_tau_convergence} (left) show that the relative error decreases as $\text{constant} \times \left(\# \text{impulse responses}\right)^{-1}$
% or $\text{constant} \times \# \text{batches}^{-1}$, 
suggesting linear convergence. The linear convergence stalls at a limit that depends on $\tau$. Increasing $\tau$ lowers this limit, allowing the PSF-based method to achieve higher accuracy. 
In Figure \ref{fig:PSF_tau_convergence} (right), the results show that before this limit is reached, the convergence is faster for smaller $\tau$ in terms of the number of batches. This is expected because smaller $\tau$ results in more impulse responses per batch. Larger $\tau$ causes the PSF-based method to converge more slowly than smaller $\tau$, but with larger $\tau$ the PSF-based method stalls at a lower level of error than it does with smaller $\tau$ (see, e.g., $\tau=4.0$ vs. $\tau=2.5$).
